%\renewcommand{\baselinestretch}{0.5}
\begin{thebibliography}{10}

\bibitem{Personalization1}
Gediminas Adomavicius and Alexander Tuzhilin. 1999.
\newblock {\em User Profiling in Personalization Applications through Rule Discovery and Validation[J]}.
\newblock ACM, 377-381.

\bibitem{Personalization2}
lbrahim Cingil, Asuman Dogac and Ayca Azgin.2000.
\newblock {\em A broader approach to personalization[J]}.
\newblock mmunications of the ACM, 43(8): 136-141.

\bibitem{Personalization3}
Joseph Kramer, Sunil Noronha and John Vergo.2000.
\newblock {\em A user-centered design approach to personalization[J]}.
\newblock Communications of the ACM, 43(8)44-48.

\bibitem{Personalization4}
Bamshad Mobasher, Honghua Dai, Tao Luo, Yuqing Sun and Jiang Zhu.2000.
\newblock {\em Integrating Web Usage and Content Mining for More Effective Personalization[J]}.
\newblock Electronic Commerce and Web Technologies, 1875: 165-176.

\bibitem{Personalization5}
Bamshad Mobasher, Robert Cooley and Jaideep Srivastava.2000.
\newblock {\em Automatic personalization based on Web usage mining[J]}.
\newblock Communications of the ACM, 43(8): 142-151.

\bibitem{Personalization6}
P. Chen, H. Xie, S. Maslov, and S. Redner.2007.
\newblock {\em Finding Scientific Gems with Google's PageRank Algorithm[J]}.
\newblock Journal of Informetrics, 1(1):8--15.

\bibitem{Personalization7}
C. Basu, H. Hirsh, and W. Cohen.1998.
\newblock {\em Recommendation as Classification: Using Social and Content-Based Information in Recommendation[J]}.
\newblock In Proc. of the 15th National Conference on Artificial Intelligence (AAAI ’98), 714–720.

\bibitem{Personalization8}
J. Teevan and S. T. Dumais and E. Horvitz.2005.
\newblock {\em Personalizing Search via Automated Analysis of Interests and Activities[J]}.
\newblock . In Proc. of the 28th Annual International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 2005), 449–456,

\bibitem{Personalization9}
S. M. McNee, I. Albert, D. Cosley, S. L. P. Gopalkrishnan, A. M.Rashid, J. S. Konstan, and J. Riedl.2002.
\newblock {\em Predicting User Interests from Contextual Information[J]}.
\newblock  In Proc. of the 2002 ACM Conference on Computer Supported Cooperative Work (CSCW ’02), 116–125,

\bibitem{recmd-system}
Francesco Ricci and Lior Rokach and Bracha Shapira.2011.
\newblock {\em Introduction to Recommender Systems Handbook[M]}.
\newblock Springer, 1-35. 

\bibitem{demo-data}
Bruce Krulwich.1997.
\newblock {\em Lifestyle finder: Intelligent user profiling using large-scale demographic data[C]}.
\newblock AI Magazine, 18(2):37–45.

\bibitem{user-interests-explore}
Agichtein, E., Brill, E. \& Dumais, S.T. (2006). 
\newblock {\em Improving web search ranking by incorporating user behavior information[J]}.
\newblock Proc. SIGIR, 19-26.

\bibitem{user-interests-explore1}
Bilenko, M. et al. (2008).
\newblock {\em Talking the talk vs. walking the walk: salience of information needs in querying vs. browsing[J]}.
\newblock Proc. ACM SIGIR, 705-706.

\bibitem{user-interests-explore2}
Broder, A. (2002).
\newblock {\em A taxonomy of Web search[J]}.
\newblock ACM SIGIR Forum, 36(2), 3-10.

\bibitem{user-interests-explore3}
Broder, A. (2002).
\newblock {\em A taxonomy of Web search[J]}.
\newblock ACM SIGIR Forum, 36(2), 3-10.

\bibitem{user-interests-explore4}
Budzik, J. \& Hammond, K. (1999).
\newblock {\em  Watson: anticipating and contextualizing information needs[J]}.
\newblock Proc. ASIS, 727-740.

\bibitem{cognitive-science}
Elaine Rich.1998.
\newblock {\em Readings in intelligent user interfaces[C]}.
\newblock chapter User modeling via stereotypes, 329–342. 

\bibitem{Forecast-principle}
J. Scott Armstrong, editor.2001.
\newblock {\em Principles of Forecasting - A Handbook for Researchers and Practitioners[M]}.
\newblock Kluwer Academic.

\bibitem{cf-sn}
Henry Kautz, Bart Selman, and Mehul Shah. March 1997.
\newblock {\em Referral web: combining social networks and collaborative filtering[C]}.
\newblock Commun. ACM, 40:63–65.

\bibitem{Amazon-cf}
Greg Linden, Brent Smith, and Jeremy York. January 2003.
\newblock {\em Amazon.com recommendation- s: Item-to-item collaborative filtering[C]}.
\newblock IEEE Internet Computing, 7:76–80.

\bibitem{info-overload}
Anne-F. Rutkowski and Carol S. Saunders.June 2010.
\newblock {\em Growing pains with information overload[C]}.
\newblock Computer, 43:96–95.

\bibitem{info-overload:1}
Anne-F. Rutkowski and Carol S. Saunders.June 2010.
\newblock {\em Growing pains with information overload[C]}.
\newblock Computer, 43:96–95.

\bibitem{recmd-history}
Liu, Yu; Li, Weijia; Yao, Yuan; Fang, Jing; Ma, Ruixin; Yan, Zhaofa.
\newblock {\em An Infrastructure for Personalized Service System Based on Web2.0 and Data Mining[J]}.
\newblock International Conference on Intelligent Computing and Information Science. JAN 08-09, 2011.

\bibitem{recmd-youtube}
Shumeet Baluja, Rohan Seth, D. Sivakumar, Yushi Jing, Jay Yagnik, Shankar Kumar, Deepak Ravichandran, and Mohamed Aly.2008.
\newblock {\em Video suggestion and discovery for youtube: taking random walks through the view graph[J]}.
\newblock In Proceeding of the 17th international conference on World Wide Web, WWW ’08, pages 895–904.

\bibitem{recmd-netflix}
Robert M. Bell and Yehuda Koren. December 2007.
\newblock {\em Lessons from the netflix prize challenge[J]}.
\newblock SIGKDD Explor. Newsl., 9:75–79.

\bibitem{user-interest}
Sia K.C, Zhu S.Chi, Hino Tseng, B.L.2006.
\newblock {\em Capturing User Interests by Both Exploitation and Exploration[C]}.
\newblock Technical report, NEC Labs America. 

\bibitem{latent-cf}
Thomas Hofmann and Jan Puzicha.1999. 
\newblock {\em Latent class models for collaborative filtering[J]}.
\newblock In Proceedings of the Sixteenth International Joint Conference on Artificial Intelligence, IJCAI ’99,San Francisco, CA, USA, Morgan Kaufmann Publishers Inc, pages 688–693, 

\bibitem{date-mining}
Han Jiawei, Kamber, Micheline.2001.
\newblock {\em Data mining: concepts and techniques[C]}.
\newblock Morgan Kaufmann. 5.

\bibitem{info-retrieval}
Jansen B.J and Rieh S.2010.
\newblock {\em The Seventeen Theoretical Constructs of Information Searching and Information Retrieval[J]}.
\newblock Journal of the American Society for Information Sciences and Technology. 61(8)

\bibitem{long-tail}
O Celma. 2010.
\newblock{\em Music Recommendation and Discovery in the Long Tail[C]}.
\newblock Springer. 

\bibitem{recmd-Hybrid}
Robin Burke. November 2002.
\newblock {\em Hybrid recommender systems: Survey and experiments[J]}.
\newblock User Modeling and User-Adapted Interaction, 12:331–370.

\bibitem{social-filter}
Henry Kautz, Bart Selman, and Mehul Shah.March 1997.
\newblock {\em Referral web: combining social networks and collaborative filtering[C]}.
\newblock Commun. ACM, 40:63–65.

\bibitem{collab-filter}
Jonathan L. Herlocker, Joseph A. Konstan, Loren G. Terveen, and John T. Riedl.January 2004.
\newblock {\em Evaluating collaborative filtering recommender systems[C]}.
\newblock ACM Trans.Inf.Syst, 22:5–53.

\bibitem{cold-start}
Andrew I.Schein, Alexandrin Popescul, Lyle H.Ungar, David M.Pennock. 2002.
\newblock {\em Methods and Metrics for Cold-Start Recommendations[C]}.
\newblock New York City, New York: ACM. 253–260.

\bibitem{user-profile}
Adams, Suellen .2005.
\newblock {\em Information Behavior and the Formation and Maintenance of Peer Cultures in Massive Multiplayer Online Roleplaying Games: a Case Study of City of Heroes[J]}.
\newblock DiGRA: Changing Views - Worlds in Play. Authors \& Digital Games research Association (DiGRA).

\bibitem{user-profile1}
Nabeth, Thierry (26 May 2006).
\newblock {\em Understanding the Identity Concept in the Context of Digital Social Environments[J]}.
\newblock FIDIS Deliverables. 2. FIDIS. pp. 74–91.

\bibitem{user-profile2}
Suler, John (2004).
\newblock {\em The Online Disinhibition Effect[J]}.
\newblock CyberPsychology \& Behavior. 7 (3): 321–326.

\bibitem{user-profile3}
Marcus, Bernd; Machilek, Franz; Schütz, Astrid (2006).
\newblock {\em Personality in cyberspace: Personal web sites as media for personality expressions and impressions[J]}.
\newblock Journal of Personality and Social Psychology. 90 (6): 1014–1031.

\bibitem{user-profile4}
Siibak, Andra (September 2007).
\newblock {\em  Casanovas of the Virtual World. How Boys Present Themselves on Dating Websites[J]}.
\newblock Young People at the Crossroads: 5th International Conference on Youth Research. Petrozavodsk, Republic of Karelia, Russian Federation. pp. 83–91.
\bibitem{recmd-kmeans}
Hartigan, J.A.Wong, M.A.Algorithm.
\newblock {\em A k-Means Clustering Algorithm[J]}.
\newblock Journal of the Royal Statistical Society, Series C. 1979, 28 (1): 100–108.

\bibitem{content-based}
K Yoshii.2006.
\newblock {\em Hybrid Collaborative and Content-Based Music Recommendation Using Probabilistic Model with Latent User Preferences [C]}.
\newblock In: Proceedings of the International Conference on Music Information Retrieval.

\bibitem{liar_taobao}
山西晚报, 科学频道.2015.
\newblock {\em 大数据揭秘：淘宝上的假货、次品都卖给了谁？}.
\newblock  http://science.china.com.cn/2015-12/01/content\_8417479.htm.

\bibitem{recmd-facebook}
Maja Kabiljo, Aleksandar Ilic. June, 2015.
\newblock {\em Recommending items to more than a billion people[DB/OL]}.
\newblock https://code.facebook.com/posts/861999383875667/recommending-items-to-more-than-a-billion-people.

\bibitem{recmd-douban}
稳国柱. 2015.
\newblock {\em 寻路推荐 豆瓣推荐系统实践之路[DB/OL]}.
\newblock http://www.36dsj.com/archives/35273.

\bibitem{recmd-doubanFM}
知乎网网友. 2011.
\newblock {\em 豆瓣 FM 的推荐算法是怎样的[DB/OL]}.
\newblock https://www.zhihu.com/question/19560538.

\bibitem{recmd-Next}
Gediminas Adomavicius, Alexander Tuzhilin. JUNE 2005.
\newblock {\em Towards the Next Generation of Recommender Systems: A Survey of the State-of-the-Art and Possible Extensions[J]}.
\newblock  IEEE transactions on knowledge and data engineering, vol. 17, no. 6.

\bibitem{Wikipedia}
From Wikipedia, the free encyclopedia.
\newblock {\em Collaborative filtering[J]}.
\newblock  https://en.wikipedia.org/wiki/Collaborative\_filtering\#Types.

\bibitem{recmd-slopone}
Daniel Lemire, Anna Maclachlan.
\newblock {\em Slope One Predictors for Online Rating-Based Collaborative Filtering[J]}.
\newblock In SIAM Data Mining (SDM'05), Newport Beach, California, April 21-23, 2005.

\bibitem{temporal-cf}
Yehuda Koren.2009.
\newblock {\em Collaborative filtering with temporal dynamics[J]}.
\newblock In Proceedings of the 15th ACM SIGKDD international conference on Knowledge discovery and data mining, KDD ’09,New York, NY, USA., pages 447–456.

\bibitem{ab-test}
Kohavi, Ron, Longbotham, Roger.2015.
\newblock {\em Online Controlled Experiments and A/B Tests[C]}.
\newblock In Sammut.

\end{thebibliography}
