%\renewcommand{\baselinestretch}{0.5}
\begin{thebibliography}{10}
\bibitem{long-tail}
O. Celma.
\newblock{\em Music Recommendation and Discovery in the Long Tail}.
\newblock Springer. 2010.

\bibitem{content-based}
Marko Balabanovi ́c and Yoav Shoham.
\newblock {\em Fab: content-based, collaborative recommendation}.
\newblock Commun. ACM, 40:66–72, March 1997.

\bibitem{cold-start}
Andrew I. Schein, Alexandrin Popescul, Lyle H. Ungar, David M. Pennock.
\newblock {\em Methods and Metrics for Cold-Start Recommendations}.
\newblock New York City, New York: ACM. pp. 253–260. 2002.

\bibitem{user-interest}
C\TeX{} Sia, K.C., Zhu, S., Chi, Y., Hino, K., Tseng, B.L.
\newblock {\em Capturing User Interests by Both Exploitation and Exploration}.
\newblock Technical report, NEC Labs America. 2006.

\bibitem{info-retrieval}
Jansen, B. J. and Rieh, S.
\newblock {\em The Seventeen Theoretical Constructs of Information Searching and Information Retrieval}.
\newblock Journal of the American Society for Information Sciences and Technology. 61(8), 2010.

\bibitem{date-mining}
Han, Jiawei; Kamber, Micheline.
\newblock {\em Data mining: concepts and techniques}.
\newblock Morgan Kaufmann. p. 5. 2001.recmd-system

\bibitem{recmd-system}
Francesco Ricci and Lior Rokach and Bracha Shapira.
\newblock {\em Introduction to Recommender Systems Handbook}.
\newblock Springer, pp. 1-35. 2011.

\bibitem{matthew-effect}
Robert K. Merton.
\newblock {\em The Matthew Effect in Science}.
\newblock Science, 159(3810):56– 63, January 1968.

\bibitem{matthew-effect:2}
Junghoo Cho and Sourashis Roy.
\newblock {\em Impact of search engines on page popularity}.
\newblock In Proceedings of the 13th international conference on World Wide Web, WWW ’04, pages 20–29, New York, NY, USA, ACM. 2004.

\bibitem{matthew-effect:3}
Daniel M. Fleder and Kartik Hosanagar.
\newblock {\em Recommender systems and their impact on sales diversity}.
\newblock In Proceedings of the 8th ACM conference on Electronic commerce, EC ’07, pages 192–199, New York, NY, USA, ACM. 2007.

\bibitem{social-filter}
Henry Kautz, Bart Selman, and Mehul Shah.
\newblock {\em Referral web: combining social networks and collaborative filtering}.
\newblock Commun. ACM, 40:63–65, March 1997.

\bibitem{collab-filter}
Jonathan L. Herlocker, Joseph A. Konstan, Loren G. Terveen, and John T. Riedl.
\newblock {\em Evaluating collaborative filtering recommender systems}.
\newblock ACM Trans. Inf. Syst., 22:5–53, January 2004.

\bibitem{ab-test}
Kohavi, Ron, Longbotham, Roger.
\newblock {\em Online Controlled Experiments and A/B Tests}.
\newblock In Sammut, Claude; Webb, Geoff. 2015.

\bibitem{cognitive-science}
Elaine Rich.
\newblock {\em Readings in intelligent user interfaces}.
\newblock chapter User modeling via stereotypes, pages 329–342. 1998.

\bibitem{info-overload}
Anne-F. Rutkowski and Carol S. Saunders.
\newblock {\em Growing pains with information overload}.
\newblock Computer, 43:96–95, June 2010.

\bibitem{Forecast-principle}
J. Scott Armstrong, editor.
\newblock {\em Principles of Forecasting - A Handbook for Researchers and Practitioners}.
\newblock Kluwer Academic, 2001.

\bibitem{cf-sn}
Henry Kautz, Bart Selman, and Mehul Shah.
\newblock {\em Referral web: combining social networks and collaborative filtering}.
\newblock Commun. ACM, 40:63–65, March 1997.

\bibitem{info-overload}
Greg Linden, Brent Smith, and Jeremy York. 
\newblock {\em Amazon.com recommendation- s: Item-to-item collaborative filtering}.
\newblock IEEE Internet Computing, 7:76–80, January 2003.

\bibitem{Amazon-cf}
Anne-F. Rutkowski and Carol S. Saunders.
\newblock {\em Growing pains with information overload}.
\newblock Computer, 43:96–95, June 2010.

\bibitem{temporal-cf}
Yehuda Koren.
\newblock {\em Collaborative filtering with temporal dynamics}.
\newblock In Proceedings of the 15th ACM SIGKDD international conference on Knowledge discovery and data mining, KDD ’09, pages 447–456, New York, NY, USA, 2009. ACM.

\bibitem{latent-cf}
Thomas Hofmann and Jan Puzicha.
\newblock {\em Latent class models for collaborative filtering}.
\newblock In Proceedings of the Sixteenth International Joint Conference on Artificial Intelligence, IJCAI ’99, pages 688–693, San Francisco, CA, USA, 1999. Morgan Kaufmann Publishers Inc.

\bibitem{demo-data}
Bruce Krulwich.
\newblock {\em Lifestyle finder: Intelligent user profiling using large-scale demographic data}.
\newblock AI Magazine, 18(2):37–45, 1997.

\bibitem{Trust-walker}
Mohsen Jamali and Martin Ester.
\newblock {\em Trustwalker: a random walk model for combining trust-based and item-based recommendation}.
\newblock In Proceedings of the 15th ACM SIGKDD international conference on Knowledge discovery and data mining, KDD ’09, pages 397–406, New York, NY, USA, ACM. 2009.

\end{thebibliography}
